Interactive Visual Analysis of Image-Centric Cohort Study Data

### 2014-06-27 draft.tex
Replaced 'features' with 'variables' in the figures

\textbf{Multivariate analysis is most important for hypothesis generation.}
Both experts emphasized the potential of the \emph{multivariate analysis} capabilities of the contingency matrix for getting insight into a large amount of variables simultaneously.
%
It is also useful to verify established but still controversial risk factors, such as the metabolic syndrome for coronary heart disease and whether the data set provides even more suitable risk factors.
%
Creating contingency matrices for subgroups, such as different age bins can help to characterize the aging process by deriving age-specific risk factors.
%
\emph{Multivariate analysis} can be improved by more ways of brushing the data as well as creating subgroups for comparison as a result of the hypothesis-driven analysis case.
%
Too small variable ranges yielding sparse groups could hinder the calculation of statistical resilient measures, since they require a minimum amount of subjects exhibiting the selected variable ranges.
%This also has to respect the number of subjects available for epidemiological studies
%
%\textbf{Hypothesis driven analysis would benefit from more advanced grouping.}
%While the existing brushing and linking techniques already allow the comparison of image data

>>>>

\textbf{Multivariate analysis is most important for hypothesis generation.}
Both experts emphasized the potential of the \emph{multivariate analysis} capabilities of the contingency matrix for getting insight into a large amount of variables simultaneously.
%
It is also useful to verify established but still controversial risk factors, such as the metabolic syndrome for coronary heart disease and whether the data set provides more suitable risk factors.
%
Creating contingency matrices for subgroups, such as different age bins can help to characterize the aging process by deriving age-specific risk factors.
%
\emph{Multivariate analysis} can be improved by more ways of brushing the data as well as creating subgroups for comparison as a result of the hypothesis-driven analysis case.
%
Too small variable ranges yielding sparse groups could hinder the calculation of statistical resilient measures, since they require a minimum amount of subjects exhibiting the selected variable ranges.
%This also has to respect the number of subjects available for epidemiological studies
%
%\textbf{Hypothesis driven analysis would benefit from more advanced grouping.}
%While the existing brushing and linking techniques already allow the comparison of image data
